Transfer of Value Functions via Variational Methods

### 2018-05-18 NIPS 2018/main.tex
Fixing to Theorem 1

\begin{restatable}{theorem}{thmm} \label{th:mm}
Let $Q^*$ be the fixed-point of the optimal Bellman operator $T$. Define the action-gap function $g(s)$ as the difference between the value of the best action and the second best action at each state $s$. Let $\wt{Q}$ be the fixed-point of the mellow Bellman operator $\wt{T}$ with parameter $\kappa > 0$ and denote by $\beta_{\kappa} > 0$ the inverse temperature of the induced Boltzmann distribution (as in \cite{asadi2017alternative}). Let $\nu$ be a probability measure over the state-action space. Then, for any $p \geq 1$:
\begin{equation}
\norm{Q^*-\wt{Q}}_{\nu,p}^p \leq\ \frac{2\gamma R_{max}}{(1-\gamma)^2}\norm{\frac{1}{1 + \frac{1}{\abs{\mathcal{A}}}e^{\beta_{\kappa} g}}}_{\nu,p}^p.
\end{equation}
\end{restatable}

The proof is provided in App. \ref{app:a1}. As expected, $\wt{Q}$ converges to $Q^*$ exponentially fast when either $\kappa$ (equivalently, $\beta_{\kappa}$) increases, or the action gaps are enlarged. Notice that this result is of interest even outside our specific settings.

@@

\end{scope}

\draw [thick, line width=0.6mm, dotted, nt] (0,-1.5) -- (1,-1.5);
\node at (1.5,-1.5) [right] {NT};
\draw [thick, line width=0.6mm, dashed,gvt] (6, -1.5) -- (7,-1.5);
\node at (7,-1.5) [right] {GVT};
\draw [thick, line width=0.6mm, mgvt1] (0,-2.5) -- (1,-2.5);
\node at (1.5,-2.5) [right] {1-MGVT};
\draw [thick, line width=0.6mm, mgvt3] (6, -2.5) -- (7,-2.5);
\node at (11.2,-2.5) [left] {3-MGVT};

\end{scope}
\end{tikzpicture} 
    \caption{The rooms problem}\label{f:rooms}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[trim=0cm 0cm 1.2cm 1.1cm,clip=true,height=2.9cm]{images/three-room/lrev.pdf}
    \caption{Rooms: two doors moving}\label{f:two_doors}
  \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[trim=0cm 0cm 1.2cm 1.1cm,clip=true,height=2.9cm]{images/three-room-gen/lrev.pdf}
    \caption{Rooms: one door moving}\label{f:one_door}
  \end{subfigure}
%    \begin{subfigure}[b]{0.27\textwidth}
%    \includegraphics[trim=0cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/likelihood/lrew.pdf}
%    \caption{}\label{f:likelihood}
%  \end{subfigure}

@@

\norm{Q^*-\wt{Q}}_{\nu,p}^p =\ & \norm{TQ^* - \wt{T}\wt{Q}}_{\nu,p}^p \\ =\ &
\norm{TQ^* - \wt{T}Q^* + \wt{T}Q^* - \wt{T}\wt{Q}}_{\nu,p}^p \\ \leq\ &
\norm{TQ^* - \wt{T}Q^*}_{\nu,p}^p + \norm{\wt{T}Q^* - \wt{T}\wt{Q}}_{\nu,p}^p \\ \leq\ &
\norm{TQ^* - \wt{T}Q^*}_{\nu,p}^p + \gamma\norm{Q^* - \wt{Q}}_{\nu,p}^p,

@@

\norm{Q^*-\wt{Q}}_{\nu,p}^p \leq \frac{1}{1-\gamma}\norm{TQ^* - \wt{T}Q^*}_{\nu,p}^p.

>>>>

\begin{restatable}{theorem}{thmm} \label{th:mm}
Let $Q^*$ be the fixed-point of the optimal Bellman operator $T$. Define the action-gap function $g(s)$ as the difference between the value of the best action and the second best action at each state $s$. Let $\wt{Q}$ be the fixed-point of the mellow Bellman operator $\wt{T}$ with parameter $\kappa > 0$ and denote by $\beta_{\kappa} > 0$ the inverse temperature of the induced Boltzmann distribution (as in \cite{asadi2017alternative}). 
% Let $\nu$ be a probability measure over the state-action space. 
Then:
\begin{equation}
\norm{Q^*-\wt{Q}}_{\infty} \leq\ \frac{2\gamma R_{max}}{(1-\gamma)^2}\norm{\frac{1}{1 + \frac{1}{\abs{\mathcal{A}}}e^{\beta_{\kappa} g}}}_{\infty}.
\end{equation}
\end{restatable}

The proof is provided in App. \ref{app:a1}. Notice that $\wt{Q}$ converges to $Q^*$ exponentially fast as $\kappa$ (equivalently, $\beta_{\kappa}$) increases and the action gaps are all larger than zero. Notice that this result is of interest even outside our specific settings.

@@

\end{scope}
\begin{scope}[shift={(1,0)}]
\draw [thick, line width=0.6mm, dotted, nt] (0,-1.5) -- (1,-1.5);
\node at (1.5,-1.5) [right] {\small NT};
\draw [thick, line width=0.6mm, dashed,gvt] (6, -1.5) -- (7,-1.5);
\node at (7,-1.5) [right] {\small GVT};
\draw [thick, line width=0.6mm, mgvt1] (0,-2.5) -- (1,-2.5);
\node at (1.5,-2.5) [right] {\small 1-MGVT};
\draw [thick, line width=0.6mm, mgvt3] (6, -2.5) -- (7,-2.5);
\node at (10.9,-2.5) [left] {\small 3-MGVT};
\end{scope}
\end{scope}
\end{tikzpicture} 
    %\caption{The rooms problem}\label{f:rooms}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[trim=0cm 0cm 1.2cm 1.1cm,clip=true,height=2.9cm]{images/three-room/lrev.pdf}
    \caption{Rooms: two doors moving}\label{f:two_doors}
  \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[trim=0cm 0cm 1.2cm 1.1cm,clip=true,height=2.9cm]{images/three-room-gen/lrev.pdf}
    \caption{Rooms: one door moving}\label{f:one_door}
  \end{subfigure}
%    \begin{subfigure}[b]{0.27\textwidth}
%    \includegraphics[trim=0cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/likelihood/lrew.pdf}
%    \caption{}\label{f:likelihood}
%  \end{subfigure}

@@

\norm{Q^*-\wt{Q}}_{\infty} =\ & \norm{TQ^* - \wt{T}\wt{Q}}_{\infty} \\ =\ &
\norm{TQ^* - \wt{T}Q^* + \wt{T}Q^* - \wt{T}\wt{Q}}_{\infty} \\ \leq\ &
\norm{TQ^* - \wt{T}Q^*}_{\infty} + \norm{\wt{T}Q^* - \wt{T}\wt{Q}}_{\infty} \\ \leq\ &
\norm{TQ^* - \wt{T}Q^*}_{\infty} + \gamma\norm{Q^* - \wt{Q}}_{\infty},

@@

\norm{Q^*-\wt{Q}}_{\infty} \leq \frac{1}{1-\gamma}\norm{TQ^* - \wt{T}Q^*}_{\infty}.
